### 2015-05-14 whoop.tex
fixes

The forms of statements are shown in Figure~\ref{fig:statements}, and include designated statements for reading from and writing to shared variables.  In particular, shared variables may not appear in arbitrary expressions.  This restriction simplifies our presentation of lockset instrumentation, below, and a program that does not satisfy this restriction can be trivially pre-processed into one that does via the introduction of additional private temporary variables to record values read from the shared state.  We do not specify the form of expressions, nor the types of variables, assuming a standard set of data types and operations.

@@

\noindent\textbf{Extracting Entry Point Information }
%
Chauffeur is a Clang-based frontend that traverses the abstract syntax tree (AST) of the original driver (using a Clang visitor pass) and extracts all entry point identifier names, together with the identifier names of their corresponding kernel API functions. Linux drivers define entry points in a standard way (see Figure~\ref{fig:entrypoints} for an example of how the generic\_nvram driver defines the entry points for the \texttt{file\_operations} API); Chauffeur identifies these definitions in the AST and outputs the relevant information in an XML file, which is subsequently parsed by \whoop and used during the instrumentation.

>>>>

The forms of statements are shown in Figure~\ref{fig:statements}, and include designated statements for reading from and writing to shared variables.  In particular, shared variables may not appear in arbitrary expressions.  This restriction simplifies our presentation of lockset instrumentation below, and a program that does not satisfy this restriction can be trivially pre-processed into one that does via the introduction of additional private temporary variables to record values read from the shared state.  We do not specify the form of expressions, nor the types of variables, assuming a standard set of data types and operations.

@@

\noindent\textbf{Extracting Entry Point Information }
%
Chauffeur is a Clang-based tool that traverses the abstract syntax tree (AST) of the original driver and extracts all entry point identifier names, together with the identifier names of their corresponding kernel API functions. Linux drivers define entry points in a standard way (see Figure~\ref{fig:entrypoints} for an example of how the generic\_nvram driver defines the entry points for the \texttt{file\_operations} API); Chauffeur identifies these definitions in the AST and outputs the relevant information in an XML file, which is parsed by \whoop to be used during the instrumentation.
